%-------------------------
% Resume in Latex
% Author : Anuj
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
 \usepackage{graphicx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}
% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Anuj} \\ \vspace{5pt}
    \small \faPhone* \texttt{+91 79.778.44759} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \url{anujkumar30dec@gmail.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faGithub \hspace{2pt} {\href{https://github.com/kanujgit}{\myuline {Github}}}\hspace{1pt} $|$
    \hspace{1pt} \faLinkedin \hspace{2pt} {\href{https://www.linkedin.com/in/anuj-kumar-7262b9113/}{\myuline {Linkedin}}
    \\ \vspace{-3pt}}
\end{center}



%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {MNNIT Allahabad}{Jul. 2014 -- May 2017}
      {Master of Computer Application}{Allahabad, U.P.}
      	\resumeItemListStart
    	\resumeItem {\textbf{Coursework}: Data Structures, Algorithms, Database, Computer Architecture and Organization, Operating System, Computer Network.}
        \resumeItem 
            {\textbf{Project}: Pollution Visualization 
\begin{itemize}
\item This android application will provide some important parameters which are used to calculate the pollution level.
\item Pollution Visualization uses JSOUP technology based data fetching technique to show pollution level of a city, provided by a trusted website.
\end{itemize}
			}
        \resumeItemListEnd
  
        \resumeSubheading
      {B.N.D. College}{Jul. 2010 -- May 2013}
      {Bachelor of Science}{Kanpur, U.P.}
      	\resumeItemListStart
    	\resumeItem {\textbf{Coursework}: Computer Application, Mathematics, Physics.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
  \resumeSubheading
      {\href{https://corp.rakuten.co.in/}{\myuline {Rakuten}}}{Nov 2021 -- Present : 5 mos}
      {Software Engineer II }{Bangalore Urban, Karnataka, india}
      \resumeItemListStart
        \resumeItem{Implemented unit test which has improved 80-90\% automation testing.}
        \resumeItem{Implemented group chat feature.}
        \resumeItem{\textbf{ Technologies used} : Java, Kotlin, Firebase, REST API, Junit} 
      \resumeItemListEnd
      
    \resumeSubheading
      {\href{https://www.algoworks.com/}{\myuline {Algoworks}}}
      {Jan 2019 -- Nov 2021 : 2 yrs 11 mos }
      {Software Engineer }{Sector - 62, Noida, india}
      \resumeItemListStart
        \resumeItem{Developed Android Applications in Kotlin from scratch using Modern Android development practices, MVVM, Retrofit, Coroutines and Architecture Components.}
        \resumeItem{99\% Crash-free rate of all applications across different OEMs.}
        \resumeItem{Improved continuous integration and continuous delivery for mobile apps resulting in 50\% increase in developer productivity.}
        \resumeItem{Architected UI of the Merlyn AI Digital application using constraint layout,to improve code quality and coverage by more than 80\% using Test Driven Development (TDD), improve maintainability and app performance}
        \resumeItem{\textbf{ Technologies used} : Java, Kotlin, Firebase, MQTT, REST API.} 
      \resumeItemListEnd

    \resumeSubheading
    {\href{https://sktuligroup.com/}{\myuline {SK Tuli Group Ltd.}}}{Feb 2018 -- Jan 2019 : 1 yr}
      {Android  Developer}{Sector-135, Noida, india}
      \resumeItemListStart
        \resumeItem{Developed Android Applications in java from scratch using Modern Android development practices, MVP, MVC, Retrofit, Volley and Architecture Components.}
        \resumeItem{Maintaining codebase and integrating new features in consumer side and provider side Android apps}
        \resumeItem{\textbf{Technologies used} : Java, Firebase suites, REST API.} 
    \resumeItemListEnd


   %-----------PROJECTS-----------
\section{PROJECTS}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{\href{https://play.google.com/store/apps/details?id=jp.co.rakuten.mobile.rcs\&hl=en_IN\&gl=US}{\myuline{Rakuten Link}} - (Rakuten)}} {Nov. 2021 -- current}
          \resumeItemListStart
            \resumeItem{Upgrade legacy code to Kotlin with coroutine for asynchronous calls.}
            \resumeItem{\textbf{Highlights: }
                Kotlin, Java, Rx-Android, Coroutine, MQTT, Espresso UI \& unit testing}
            
          \resumeItemListEnd
          

      \resumeProjectHeading
          {\textbf{\href{https://www.merlyn.org/product}{\myuline{Merlyn AI Digital Assistant}} - (Algoworks)}} {Aug. 2019 -- current}
          \resumeItemListStart
            \resumeItem{Designed a \textbf{collaborative learning ecosystem} for students and teachers with Google voice API.}
            \resumeItem{Designed a app sharing data lib with help of content provider api which \textbf{increase sharing data} limit in offline and online mode.}
            \resumeItem{\textbf{Highlights: }
                Kotlin, Java, RxAndroid, Coroutine, MQTT, Espresso UI Testing}
            
           
          \resumeItemListEnd
          
         
          \resumeProjectHeading
          {\textbf{\href{https://play.google.com/store/apps/details?id=main.ClicFlyer\&hl=en_IN\&gl=US}{\myuline{Shopping \& Offers App: ClicFlyer}} - (Algoworks)}}{Jul. 2020 -- Dec. 2020}
          \resumeItemListStart
            \resumeItem{Implemented scoped storage framework in app which increased software reliability for higher versions of Android.}
            \resumeItem{Developed an invite feature in the Android app; 20\% of new users came through app invitations.}
            \resumeItem{\textbf{Highlights: }
                Kotlin, Java, RxAndroid, Firebase Push Notification, Timber, Room, Junit testing. }
          \resumeItemListEnd
          
          
    
      \resumeProjectHeading
         {\textbf{\href{https://play.google.com/store/apps/details?id=com.benoholding.beno}{\myuline{Cab Booking App - Beno}} - (Algoworks)}}{Mar. 2019 -- Aug. 2019}
          \resumeItemListStart
            \resumeItem{After gathering all the requirements from the client built the app from scratch.}
            \resumeItem{Suggest and added fingerprint touch access to the app which reduces app login time and it is easier for the users.}
            \resumeItem{Created a custom calendar lib which turned out to be the most loved feature in an app and it easy for users to book the cars.}
            \resumeItem{\textbf{Highlights: }
                Java, RxAndroid, Firebase Push Notification \& storage, Timber, Room, Junit testing.}
          \resumeItemListEnd
          
          
          \resumeProjectHeading
          {\textbf{\href{https://play.google.com/store/apps/details?id=com.twinsdigital.v2}{\myuline{Health tracking App - Twin}} - (Algoworks)}}{Jan. 2019 -- Mar. 2019}
          \resumeItemListStart
            \resumeItem{Implement offline video feature to the app and saved the video file in an \textbf{encrypted mode} which \textbf{reduces the app size} and is accessible only through the app.}
            \resumeItem{Increased unit test cases for components and directives using the JUnit test framework to improve the coverage from
47\% to 76\%.}
            \resumeItem{\textbf{Highlights: }
                Java, RxAndroid, Firebase Push Notification, Timber, \href{https://github.com/kanujgit/ExoPlayer}{\myuline{ExoPlayer}}, Junit testing.}
          \resumeItemListEnd
          
          
          
          \resumeProjectHeading
          {\textbf{\href{https://play.google.com/store/apps/details?id=com.kibakibipoint.kibakibipoint}{\myuline{Local shopping and ordering app}} - (SK Tuli Group Ltd.)}}{Feb. 2018 -- Jan. 2019}
          \resumeItemListStart
            \resumeItem{Implement multilingual feature which increases app accessibility in local area about 40\%. } 
            \resumeItem{\textbf{Highlights: }
                Java, Firebase Push Notification, Sqlite}
          \resumeItemListEnd
          
          
           \resumeProjectHeading
             {\textbf{others apps}}{}
                \resumeItemListStart
                    \resumeItem{{\textbf{\href{https://play.google.com/store/apps/details?id=com.algoworks.pubit}{\myuline{Events Search App - Pubit}}}}}
                    \resumeItem{{\textbf{\href{https://play.google.com/store/apps/details?id=com.neil.fakeit}{\myuline{Photo editing App - FakeIt}}}}}
                    
                    \resumeItem{{\textbf{\href{https://play.google.com/store/apps/details?id=com.axan.visyt}{\myuline{Restaurant book & search App - Visyt}}}}}
                    
                \resumeItemListEnd
            
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{SOFTWARE EXPOSURE AND SKILL}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Kotlin, XML, Sqlite}\vspace{2pt} \\
     \textbf{Tools}{: Andorid Studio, Ecplise, Figma, Jira, Basecamp, Trello, Google Analytics, Git, GitHub, Bitbucket}} \\
    \textbf{Mobile APIs}{: Room, PushNotification(FCM), GoogleMaps, AdMob, Firebase \color{white} Localization, Dragger, Hilt}}\\
    \textbf{Social Api's}{: Facebook, Gmail, Twitter, Instagram, Truecaller }\\
    \textbf{Network Api's}{: Retrofit, Volley \color{white} Okhttp,Glide,Picasso RxAndroid, Memory management, Test cases} \\
    \textbf{Testing Frameworks}{: JUnit, Espresso, Robolectric}\\
    \textbf{Architecture Design Pattern}{: MVVM, MVP, MVC}\\
    \textbf{Continuous Integration}{: CircleCi \color{white} Jenkins}\\
    \textbf{Other's}{: RxJava, Coroutine, Livedata, DataBinding \color{white} View Binding,Material Design,Socket connection, Network Profiler, memory management, ButterKnife,REST, SOAP, K-SOAP(JSON AND XML)., Gradle}
 \end{itemize}
 
 \section{ACHIEVEMENTS}
 \begin{itemize}[leftmargin=0in, label={}]
     \small\item {
     \textbf{Problem Solving}{: Solved 200+ questions on {\href{https://leetcode.com/anuj29/}{\myuline{LeetCode}}}, GeeksForGeeks and active participation in Algorithmic contests.}
     }\\
     \textbf{\href{https://www.udemy.com/certificate/UC-f55fed86-d5c3-4391-a2b3-701a772a3485/}{\myuline{Kotlin Coroutines development course}}}{: Completed  5-hour long project based certification.}\\
     \textbf{\href{https://cutshort.io/certificate/53271}{\myuline{Cutshort skill certificate}}}{: \textbf{Advanced level proficiency} Android development in Cutshort exam.}
     
    
     
 \end{itemize}

%------------------------------------------- end----------------------------------------------%


\end{document}
